---
title: "032921ChooseEnvVarsMadrone"
author: "Renata Poulton Kamakura"
date: "March 29, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(vip)
#read-in functions to calucate growth and mortality
source("../04ProcessingCode/AnalysisFunctions_GRMort.R")

options(stringsAsFactors = FALSE)

#Names
years <- c(12, 13, 14, 15)

#Ecoregion data
ecoregdat <- read.csv("../01ExampleRawData/02LocationData/EcoregionData.csv")
ecoregions <- unique(ecoregdat$EcoregionShort)

sites <- c("PuyallupHill", "PuyallupValley", "Starker", "Sprague")

#Sources
sources <- unique(ecoregdat$Source)

##Get the full data files
pertfiles <- list("../03ExampleCleanedData/PVFulldata.csv", "../03ExampleCleanedData/PHFulldata.csv",  "../03ExampleCleanedData/SFFulldata.csv", "../03ExampleCleanedData/SOFulldata.csv")
sitesdata <- lapply(pertfiles,read.csv)
names(sitesdata) <- sites


locandclim <- read.csv("../01ExampleRawData/02LocationData/LocandClim_sa.csv")

a <- length(locandclim[,1])
cg_locandclim <- locandclim[c((a-3):a),]

```

##Environmental Variables

```{r variables from ClimateNA and WNA}
GrowthRates <- PercGrowth_byTree(sitesdata, years, sites, type="sub") 
condata <- IndivCond_final(sitesdata, sites)

#WeatherData

fullClim <- read.csv("../01ExampleRawData/02LocationData/WeatherData.csv")

#find the actual climate variables in the dataframe
#here we are using seasonal and annual vriables
grdbk_climvars <- c(3, 10:13, 21:99)
cond_climvars <- c(7:11, 20:98)

#data storage matrix
stomat <- as.data.frame(matrix(0, nrow=length(grdbk_climvars), ncol= c(3*4 + 1)))
colnames(stomat) <- c("ClimVar", "PVGr", "PVDBK", "PVMort", "PHGr", "PHDBK", "PHMort", "SFGr", "SFDBK", "SFMort", "SOGr", "SODBK", "SOMort")


#Iterate through the sites
for (s in 1:4){
  
  grdbk <- merge(GrowthRates[[s]], fullClim, by="Family")
  cond <- merge(condata[[s]], fullClim, by="Family")
  
  site_ind <- (s - 1)*3 + 2 #weird but gives you the column position
  
  for (v in 1:length(grdbk_climvars)){
    
    #grad one of the climate variables
    gd_ind <- grdbk_climvars[v]
    m_ind <- cond_climvars[v]
    
    #run the linear regressions
    gr_lm <- lm(grdbk$TotGrowth ~ grdbk[,gd_ind])
    dbk_lm <- lm(grdbk$AmntDieback ~ grdbk[,gd_ind])
    mort_lm <- lm(cond$PercDead ~ cond[,m_ind])
    
    var_nm <- names(grdbk)[gd_ind]
    
    #store in the matrix
    stomat[v,1] <- var_nm
    stomat[v,site_ind] <- summary(gr_lm)$r.squared
    stomat[v,c(site_ind + 1)] <- summary(dbk_lm)$r.squared
    stomat[v,c(site_ind + 2)] <- summary(mort_lm)$r.squared
    
    
    
    
  }
  
  
}

write.csv(stomat, "../05ProcessedDataOutputs/01EnvVars/LinREgressions.csv")



```

The variables with r2 > 0.1 at at least two sites, in decreasing order of sum of r2 values across
growth, dieback, and mortality at all sites (for the original data):

Ecoregion
DD.5_wt
Tmax_wt
Eref_wt
MCMT
DD.5_at
Tave_wt
DD.18_wt
Dist
Tave_at
DD.18_at
DD.18
DD.5
MAT
SHM
Tmax_at
CMD_at
Eref_at
eFFP.y
DD.5_sp
DD.18_at.1
Tave_sp
DD.18_sp
Tmin_at
Tmin_wt
PPT_sm
CMD
CMD_sp
EMT
Eref_sp
MSP.y


Note: because here you are using simulated data, your results will not be the same. 
Change the variables of interest in "varlist" below to focus on those that provide
promising R2 values above



```{r env corr between}
#fullClim <- read.csv("../Climate Data/WeatherData.csv")
#ecoregdat
#locandclim

#all the variables of interest
varlist <- c("Latitude", "Longitude", "Slope", "Aspect", "Elevation", "DD.5_wt", "Tmax_wt", "Eref_wt", "MCMT", "DD.5_at", "Tave_wt", "DD.18_wt", "Tave_at", "DD.18_at", "DD.18", "DD.5", "MAT", "SHM", "Tmax_at", "CMD_at", "Eref_at", "eFFP.y", "DD.5_sp", "DD.18_at.1", "Tave_sp", "DD.18_sp", "Tmin_at", "Tmin_wt", "PPT_sm", "CMD", "CMD_sp", "EMT", "Eref_sp", "MSP.y", "bFFP.x")

##pairwise linear regressions
AllClim <- merge(locandclim, fullClim, by="Family")
#AllClim <- merge(AllClim, ecoregdat, by="Family")
var_inds <- match(varlist, names(AllClim))

#for iterating/comparisons
used_inds <- c()

#storage
output_mat <- as.data.frame(matrix(0, nrow=length(varlist), ncol=length(varlist)))
names(output_mat) <- varlist
rownames(output_mat) <- varlist

for (i in 1:length(varlist)){
  
  #first variable for comparison
  var1 <- AllClim[,var_inds[i]]
  var1_nm <- varlist[i]
  
  #get a list of other climate variables to compare it to
  used_inds <- append(used_inds, i)
  v_inds <- var_inds[-c(used_inds)]
  
  if (length(v_inds) != 0){
    
    for (i2 in 1:length(v_inds)){
    
    var2 <- AllClim[, c(v_inds[i2])]
    var2_nm <- varlist[match(v_inds[i2], var_inds)]
    
    corr <- summary(lm(var1 ~ var2))$r.squared #get the r.squared value
    
    output_mat[var1_nm, var2_nm] <- corr
    } 
  }else {
    next
  }
  #iterate through those other variables
  
}

write.csv(output_mat, "../05ProcessedDataOutputs/01EnvVars/ClimateVarCorrelations.csv")


```

##adding dist

```{r }
##Adding the distance to the common garden site

for (s in 1:4){
  
  grdbk <- merge(GrowthRates[[s]], fullClim, by="Family")
  
  r2_DD18 <- summary(lm(DD.18_at ~ Dist, data=grdbk))$r.squared
  r2_DD5 <- summary(lm(DD.5_sp.y ~ Dist, data=grdbk))$r.squared
  
  print(paste("At Site", s, "R2 for DD.18_at is:", r2_DD18 ))
  print(paste("At Site", s, "R2 for DD.5_sp is:", r2_DD5 ))
}

```

##Add extra variable to DD.5_sp

```{r adjust vars}
##pairwise linear regressions
f_clim <- fullClim[, c("Family", "DD.5_sp")]
ClimWNew <- merge(locandclim, f_clim, by="Family")

write.csv(ClimWNew, "../01ExampleRawData/02LocationData/LocClim.csv")

```
